**Title:** Exploring the effects of BCG vaccination in patients diagnosed with tuberculosis: observational study using the Enhanced Tuberculosis Surveillance system

### 2018-06-13 output/Paper.Rmd
added doi link
updated csl style for vaccines

---
title: '**Title:** Exploring the effects of BCG vaccination in patients diagnosed with tuberculosis: observational study using the Enhanced Tuberculosis Surveillance system'
author: "Sam Abbott, Hannah Christensen, Maeve K Lalor, Dominik Zenner, Colin Campbell, Mary Ramsay, Ellen Brooks-Pollock"
csl: ../common/bmj.csl
output:
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 8
    reference_docx: ../common/style.docx
  html_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 8
  pdf_document: default
  html_notebook: null
bibliography: ../common/library.bib
---

@@

The code for the analysis contained in this paper can be found at: [https://github.com/seabbs/ExploreBCGOnOutcomes](https://github.com/seabbs/ExploreBCGOnOutcomes)

>>>>

---
title: '**Title:** Exploring the effects of BCG vaccination in patients diagnosed with tuberculosis: observational study using the Enhanced Tuberculosis Surveillance system'
author: "Sam Abbott, Hannah Christensen, Maeve K Lalor, Dominik Zenner, Colin Campbell, Mary Ramsay, Ellen Brooks-Pollock"
csl: ../common/vaccines.csl
output:
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 8
    reference_docx: ../common/style.docx
  html_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 8
  pdf_document: default
  html_notebook: null
bibliography: ../common/library.bib
---

@@

The code for the analysis contained in this paper can be found at: [doi.org/10.5281/zenodo.1213800](doi.org/10.5281/zenodo.1213800)
